---
title: "5or7"
output: html_document
---


A nice function to visualize the row in question
```{r}
trainData = read.csv("train_data.csv")
testData = read.csv("test_data.csv")
see <- function(rowNum){
m = matrix(data.matrix(subset(testData[rowNum,],select = 3:785), rownames.force = NA),28,28)
image(m)
}


```


```{r}
summary(cars)
setwd("/Users/Tom/R/MachineLearning")
trainData = read.csv("train_data.csv")
testData = read.csv("test_data.csv")

trainData = trainData[,-1]
testData = testData[,-1]


#Train Dat Model
trainData$label = as.factor(trainData$label)
Reg = glm(label~.,data=trainData, family=binomial)

glm.probs = predict(Reg, testData ,type="response")
glm.pred=rep("8",40)
glm.pred[glm.probs >.5]=" 6"
total = 0
for (i in 1:40){
  cat(" ",glm.pred[i],"")
  n <- readline(prompt="Correct?: ")
  total = total + as.integer(n)
}

#18/40 Is the current accuracy of the logistic regression


```


Prints each plot to a pdf
```{r, echo=FALSE}
  pdf("Plots")
for(i in 1:40){

  see(i)
}
dev.off()
```


Attempt to create larger graphs with images, the idea is the number will be more centered
```{r, echo=FALSE}
#Lets try creating a new Training Dataset

#Process to create a column of zeros
emptyList = list()
zeroAdd = list(0)
for(i in 1:200){
  emptyList = append(emptyList,zeroAdd)
}
ZeroCol <- data.frame(matrix(unlist(emptyList), nrow=200, byrow=T),stringsAsFactors=FALSE)


labels = data.frame(trainData$label)
justTrainData <- subset( trainData, select = -c(label))

#Adding 100 zero columns to both the left and right of the pixel data. In an effort to simply center the image

for(i in 1:100){
 justTrainData <- cbind(ZeroCol,justTrainData)
justTrainData <- cbind(justTrainData,ZeroCol)
  
}



```


Visulizing the scaled up images
```{r, echo=FALSE}
z = matrix(data.matrix(justTrainData[20,],rownames.force = NA), 28,28)
image(z)
```


Lets Try Training the Logistic Regression with the addtion of 100 variables in each Direction from the image data. The goal here is to center the image. 
```{r, echo=FALSE}

trainData = justTrainData

trainData$label = as.factor(trainData$label)
Reg = glm(label~.,data=trainData, family=binomial)

glm.probs = predict(Reg, testData ,type="response")
glm.pred=rep("8",40)
glm.pred[glm.probs >.5]=" 6"
total = 0
for (i in 1:40){
  cat(" ",glm.pred[i],"")
  n <- readline(prompt="Correct?: ")
  total = total + as.integer(n)
}

#24/40 Slight Improvement. 
#This result is a bit suprising, because it actually increases
#the rank deficiency of the matrix. 


```


Perhaps the Solution is to Scale the nonzero values to 1

```{r, echo=FALSE}
trainData = read.csv("train_data.csv")
trainData = trainData[,-1]
labels = data.frame(trainData$label)
trainData<- trainData*0.25
#Now lets TRAIN THAT LOGISTIC MODEL

trainData$label = as.factor(trainData$label)
Reg = glm(label~.,data=trainData, family=binomial)

glm.probs = predict(Reg, testData ,type="response")
glm.pred=rep("8",40)
glm.pred[glm.probs >.5]=" 6"
total = 0


#Tried Scaling the data by 1000
#22/40, slightly worse

#Tried Scaling by 100
#20/40, even worse

#Tried Scaling by 0.25
#24/40, same result as centering




```